Toward \earlywarning\ detection of gravitational waves from compact binary coalescence

### 2011-07-11 method.tex
"may" --> "can" x3
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1285 ccdd05d5-56c1-461a-bf98-85f6876523b4

An inspiral signal will enter the detection band with some low frequency
$f_\mathrm{low}$ at time $t_\mathrm{low}$ before merger.  Usually the template
is truncated at some prescribed time $t^0$, or equivalent frequency $f_\mathrm{high}$,
often chosen to correspond to the \ISCO. The beginning of the template is critically
sampled at $2 f_\mathrm{low}$, but the end of the template is critically sampled at a
rate of $2 f_\mathrm{high}$. In any time interval smaller than the duration of the template,
the bandwidth of the filters across the entire template bank may be significantly less
than the full sample rate at which data is acquired.

@@

The time sliced templates may then be downsampled in each interval without
aliasing, so we define them as
%
\begin{equation}
\label{eq:time-sliced-templates}
h_{i}^{s}[k] \equiv
	\begin{cases}
		h_{i}\!\left[k\frac{f}{f^s}\right] & \textrm{if } t^s \leqslant k/f^s < t^{s+1} \\
		0 & \textrm{otherwise.}
	\end{cases}
\end{equation}
%
We note that the time slice decomposition in equation~(\ref{eq:time-slices}) is
manifestly orthogonal since the time slices are disjoint in time.  In the next
section we examine how to reduce the number of filters within each time slice
via \SVD{} of the time-sliced templates.

@@

In the limit of many templates, $M \gg 1$, we may neglect the cost of the forward
transform of the data and of the multiplication of the transforms.  The computational
cost will reach an optimum at some large but finite \fft\ block size
$\fftblock \gg \tmpsamps$.  In this limit, the \FD\ method costs
$\approx 2 f^0 \numtmps \lg \fftblock$ \flops.

>>>>

An inspiral signal will enter the detection band with some low frequency
$f_\mathrm{low}$ at time $t_\mathrm{low}$ before merger.  Usually the template
is truncated at some prescribed time $t^0$, or equivalent frequency $f_\mathrm{high}$,
often chosen to correspond to the \ISCO. The beginning of the template is critically
sampled at $2 f_\mathrm{low}$, but the end of the template is critically sampled at a
rate of $2 f_\mathrm{high}$. In any time interval smaller than the duration of the template,
the bandwidth of the filters across the entire template bank can be significantly less
than the full sample rate at which data is acquired.

@@

The time sliced templates can then be downsampled in each interval without
aliasing, so we define them as
%
\begin{equation}
\label{eq:time-sliced-templates}
h_{i}^{s}[k] \equiv
	\begin{cases}
		h_{i}\!\left[k\frac{f}{f^s}\right] & \textrm{if } t^s \leqslant k/f^s < t^{s+1} \\
		0 & \textrm{otherwise.}
	\end{cases}
\end{equation}
%
We note that the time slice decomposition in equation~(\ref{eq:time-slices}) is
manifestly orthogonal since the time slices are disjoint in time.  In the next
section we examine how to reduce the number of filters within each time slice
via \SVD{} of the time-sliced templates.

@@

In the limit of many templates, $M \gg 1$, we can neglect the cost of the forward
transform of the data and of the multiplication of the transforms.  The computational
cost will reach an optimum at some large but finite \fft\ block size
$\fftblock \gg \tmpsamps$.  In this limit, the \FD\ method costs
$\approx 2 f^0 \numtmps \lg \fftblock$ \flops.
